Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-07-17 dis_clusion.tex

This work has investigated the possibility to chain centrifuge enrichment
cascades designed to enrich uranium for commercial reactors in order to
produce \gls{HEU}. Three methods have been implemented to model enrichment
cascade behavior when fed with different uranium enrichment than the designed
enrichment.

@@

For this study, the use of the Cyclus fuel cycle simulator was not
required, it only allows a quick determination of the blending equilibrium. It
is planned to make use of the full capability of Cyclus Dynamical Resource Exchange 
in order to automatically assign the different cascades to the different level
as function of the resources availability, optimising the productions rates in
each cases.

>>>>

This work has investigated the possibility to chain centrifuge enrichment
cascades that are designed to enrich uranium for commercial reactors in order to
produce \gls{HEU}, instead. Three methods have been implemented to model enrichment
cascade behavior when fed with different uranium enrichment than the designed
enrichment.

@@

For this study, the use of the Cyclus fuel cycle simulator was not required;
it only allows a quick determination of the blending equilibrium. Future
studies will make use of the full capability of Cyclus Dynamic Resource
Exchange in order to automatically assign the different cascades to the
different level as function of the resources availability, optimising the
productions rates in each cases.

### 2018-07-17 results.tex

Model       &        &            & A/NR      & A/R       & B/NR      & B/R      & C/NR       & C/R       \\
%Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
\midrule                                                                                                 
        &            & Feed       & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.33w\%$ \\
Level 0 & Assay      & Product    & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $4.82w\%$ \\
        &            & Tails      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.55w\%$ \\
        & Cascades   & Real(Ideal)& 25(26.7)  & 25(26.4)  & 25(26.6)  & 24(25.8)  & 25(26.7)  & 25(26.4)  \\
\midrule                                                                                                 
        &            & Feed       & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $12.2w\%$ \\
Level 1 & Assay      & Product    & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $58.5w\%$ \\
        &            & Tails      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $6.52w\%$ \\
        & Cascades   & Real(Ideal)& 3(2.9)    & 4(3.2)    & 3(2.9)    & 4(3.4)    & 3(2.9)    & 4(3.2)    \\
\midrule                                                                                                 
        &            & Feed       & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $58.5w\%$ \\
Level 2 & Assay      & Product    & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $97.0w\%$ \\
        &            & Tails      & $4.13w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $53.8w\%$ \\
        & Cascades   & Real(Ideal)& 1(0.3)    & 1(0.3)    & 1(0.4)    & 1(0.6)    & 1(0.3)    & 1(0.35)   \\
\midrule                                                                                                 
        &            & Feed       & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
Level 3 & Assay      & Product    & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
        &            & Tails      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
        & Cascades   & Real(Ideal)& 1(0.03)   & N.A.      & 1(0.08)   & 1(0.2)    & 1(0.03)   & N.A.      \\
\bottomrule
\end{tabular}
  \label{tab:level}
\end{table}

As illustrated in Figures \ref{fig:assays} and summarized on Tab
\ref{tab:level}, the different model don't have the same effect on the cascade
behavior. While the models A and C, achieve a quick enrichment gain, with the
cascades chaining, 4/23/78/98 and 4/23/82/99 respectively, model B, only
achieves an enrichment gain of 4/21/61/90.

>>>>

Model       &        &            & A/NR      & A/R       & B/NR      & B/R      & C/NR       & C/R       \\
%Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
\midrule                                                                                                 
        &            & Feed       & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.33w\%$ \\
Level 0 & Assay      & Product    & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $4.82w\%$ \\
        &            & Tails      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.55w\%$ \\
        & Cascades   & Impl. (Ideal)& 25(26.7)  & 25(26.4)  & 25(26.6)  & 24(25.8)  & 25(26.7)  & 25(26.4)  \\
\midrule                                                                                                 
        &            & Feed       & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $12.2w\%$ \\
Level 1 & Assay      & Product    & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $58.5w\%$ \\
        &            & Tails      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $6.52w\%$ \\
        & Cascades   & Impl. (Ideal)& 3(2.9)    & 4(3.2)    & 3(2.9)    & 4(3.4)    & 3(2.9)    & 4(3.2)    \\
\midrule                                                                                                 
        &            & Feed       & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $58.5w\%$ \\
Level 2 & Assay      & Product    & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $97.0w\%$ \\
        &            & Tails      & $4.13w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $53.8w\%$ \\
        & Cascades   & Impl. (Ideal)& 1(0.3)    & 1(0.3)    & 1(0.4)    & 1(0.6)    & 1(0.3)    & 1(0.35)   \\
\midrule                                                                                                 
        &            & Feed       & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
Level 3 & Assay      & Product    & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
        &            & Tails      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
        & Cascades   & Impl. (Ideal)& 1(0.03)   & N.A.      & 1(0.08)   & 1(0.2)    & 1(0.03)   & N.A.      \\
\bottomrule
\end{tabular}
  \label{tab:level}
\end{table}

As illustrated in Figures \ref{fig:assays} and summarized on Table
\ref{tab:level}, the different models don't have the same effect on the
cascade behavior. While models A and C, achieve a quick enrichment gain with
the cascades chaining, 4/23/78/98 and 4/23/82/99, respectively, model B, only
achieves an enrichment gain of 4/21/61/90.  This table also shows the integer
number of cascades implemented (Impl.) at each level in the simulation, as well as the
non-integer number of cascades that would achieve an ideal configuration (Ideal).

### 2018-07-17 theory.tex

As the cut values change, the relative flow rates between the different stage
are recomputed using equation \eqref{eq:flow}. 
The new relative flow rates are compared stage by stage to the flow rates allowed by the
cascade design, the number of centrifuges per stage limiting the flow. The new
absolute flow rates are computed by scaling the relative flow rates using the most
limiting stage.

>>>>

As the cut values change, the relative flow rates between the different stages
are recomputed using equation \eqref{eq:flow}.  Under this model, the flow at
each stage of the original ideal cascade is assumed to be the maximum flow
allowed at that stage.  Therefore, all of the recomputed flow rates are scaled
together to ensure that no stage experiences a flow rate larger than that of
the original cascade.  Some stages may now experience flow rates much lower
than the original cascade.
